---
title: "CATS_cam_EDA"
author: "JHMoxley"
date: "9/13/2018"
output:
  html_document: default
  pdf_document: default
params:
  SI: yes
  datFreq: 50
  datFreq.desired: 1
  dd: /Volumes/Avalon
  deploy.key: APT_CC0704_20180803
  sensors: c("acc", "mag")
  smoothing: 5
  utc.offset: -7
---
This is a generalized EDA document for quickly working up biologging deployments returned from CATS tags on White Sharks.  Test built on APT_CC0705_07182018, based on EDA files associated with this deployment. 

rmarkdown::render('CATS_preprocess_RMrkD.Rmd',params= list( deploy.key = "APT_CC0705_07182018"))

```{r}
params
```

##Workup
-needs to be able to trim data 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("tag_fxns.R")
library(tidyverse)
setwd(file.path(params$dd, params$deploy.key))
#create EDA folder??
#good way to track what generation of tag fxns it used?  

#load in data
ifelse(isTRUE(params$SI), 
       print("reading in SI converted data"),
       print("reading in RAW data"))
dat <- load.in2(dir = ifelse(isTRUE(params$SI),
             str_subset(list.dirs(), "(SI)"),
             getwd()), 
             sensors = params$sensors, fstop = 2)
```

## Smoothing, isolation & manipulation

```{r}
df <- dat$dat
#smooth depth
dat$data$depth <- stats::filter(subset(dat$data, select = dat$sensors$depth[1]),
                               filter = rep(1,params$smoothing*dat$sensors$sfreq)/
                                 (params$smoothing*dat$sensors$sfreq), sides = 2, circular = T)
#smooth temp reading from depth sensor
dat$data$temp.dep <- stats::filter(subset(dat$data, select = dat$sensors$depth[2]),
                               filter = rep(1,params$smoothing*dat$sensors$sfreq)/
                                 (params$smoothing*dat$sensors$sfreq), sides = 2, circular = T)
#smooth temp imu
dat$data$temp.dep <- stats::filter(subset(dat$data, select = dat$sensors$temp),
                               filter = rep(1,params$smoothing*dat$sensors$sfreq)/
                                 (params$smoothing*dat$sensors$sfreq), sides = 2, circular = T)

plot(x = 1:nrow(dat$data), y = dat$data$depth, type = "l", main = params$deploy.key)
```

## Accelerometry
-currently not making explicit call from UI params list
-where to do pitch/roll (requires accel.. shld mandate accel sensor?)

```{r pressure, echo=FALSE}
library(gRumble)
if(any(str_detect(params$sensors, "^a|A(?=c|C)"))){
  #isolate gravitation
  gees <- data.frame(Gsep(as.matrix(subset(dat$data, select = dat$sensors$acc)), 
                          filt = (rep(1, params$smoothing*dat$sensors$sfreq))/(params$smoothing*dat$sensors$sfreq)))
  #pitchroll
  pr <- pitchRoll(gees, degrees = F)
  #downsample
  g.ds <- data.frame(apply(gees, 2, gRumble::collapse, 
                         freq = dat$sensors$sfreq/params$datFreq.desired))
  pr.ds <- data.frame(apply(pr, 2, gRumble::collapse, 
                         freq = dat$sensors$sfreq/params$datFreq.desired))
}else{
  warning("ACCEL SENSORS WERE NOT INCLUDED IN PARAMS")
}
```


## Magnetometry
-based on an email with CFW, 9/5/2018
-not confirmed this works in raw units
-need to double check declination adjustment
```{r}
if(any(str_detect(params$sensors, "^m|M(?=a|A)"))){
  #PUT THIS IN TAG_FXNS?
  err <- function(vars){
    #seq call is rough/tumble downsample to speed things up
    m <- as.matrix(subset(dat$data, select=dat$sensors$mag))
    return(sd(((m[seq(1, nrow(m), dat$sensors$sfreq),1] - vars[1]^2)+  #mx
           m[seq(1, nrow(m), dat$sensors$sfreq),2] - vars[2]^2)+       #my
           m[seq(1, nrow(m), dat$sensors$sfreq),3] - vars[3]^2))}     #mz
    
  out <- optim(c(1,1,1), fn = err)  #out$par is the center of the mag data
  
  mmms <- data.frame(Gsep(as.matrix(subset(dat$data, select = dat$sensors$mag)), 
                          filt = (rep(1, params$smoothing*dat$sensors$sfreq))/(params$smoothing*dat$sensors$sfreq)))
  #downsample
  m.ds <- data.frame(apply(mmms, 2, collapse, 
                         freq = dat$sensors$sfreq/params$datFreq.desired))
  
  #calc heading
  h.ds <- magHead(PR = pr.ds, magxyz = m.ds, magOff = out$par)
  #declination at santa cruz ~13.2 deg
  declination <- DescTools::DegToRad(13.2)
  print("USING DECLINATION ANGLE FOR SANTA CRUZ")
  h.ds <- h.ds + pi + declination
}else{
  warning("MAG SENSORS WERE NOT INCLUDED IN PARAMS")
}
```

##GYROMETER
in dev now
```{r}
if(any(str_detect(params$sensors, "^g|G(?=y|Y)"))){
  #IN DEV
}else{
  warning("GYRO SENSORS WERE NOT INCLUDED IN PARAMS")
}
```

##PLOTS
-ttdr plot needs added functionality for local offsets
```{r}
library(lubridate)
x <- as.data.frame(cbind(dts = dat$data$dts[seq(1, nrow(dat$data), dat$sensors$sfreq/params$datFreq.desired)],
                   apply(subset(dat$data, select = c("depth", "temp.dep")), 2, collapse, 
                         freq = dat$sensors$sfreq/params$datFreq.desired)))
ttdr <- ttdr.plot(x)
ttdr
```

